---
name:  
surname: Rayna Harris, PhD
position: "          "
#address: "Alpine Meadows, CA"
phone: 512-657-2964
www: www.raynaharris.com
email: "rayna.harris@gmail.com "
twitter: raynamharris
#github: raynamharris
linkedin: raynamharris
#date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
headcolor: 414141
docname: "`r format(Sys.time(), '%B %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(rorcid)
library(tidyverse)
```

# Summary

I am interested in the Director of Fitness & Dance Programs at Tahoe Flow Arts & Fitness. I have a PhD in Cell and Molecular Biology and ten years of experience managing projects, analyzing data, and communicating with diverse audiences. I am a 200-hour Yoga Alliance certified yoga instructor, and I aspire to teach beach yoga this summer. In addition to teaching biology, I also have experience teaching a computational biology instructor training program.

# Education


```{r}

edu <- do.call("rbind",
  rorcid::orcid_educations("0000-0002-7943-5650")$`0000-0002-7943-5650`$`affiliation-group`$summaries
)
edu %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`,
    where = glue::glue("{`education-summary.organization.address.city`}, {`education-summary.organization.address.region`}")
  )
```
# Certifications

```{r certification}

tribble(
  ~Year, ~Type, ~Desc, ~City, 
  "2024", "200-hour Hatha Yoga Teacher Training", "Palisades Yoga", "Olympic Valley, CA"
) %>% 
  vitae::detailed_entries(
    Type,
    Year, 
    Desc,
    City
  )

```

# Current Employment

```{r employment2}
tribble(
  ~ what, ~ when, ~ with, ~ where, ~why,
  "Mountain Host Lead", "Oct 2023 - Current",  "Palisades Tahoe at Alpine Meadows", "Alpine Meadows, CA", c("Provide a friendly and welcoming environment for guests and provide customer service", "Manage a team of 20 employees and assist other departments as needed"),
 "Adjunct Faculty, Biology and Chemistry Departments", "Jan 2023 - June 2024", "Lake Tahoe Community College", "South Lake Tahoe, CA", c("Develop course syllabi, lesson plans, and assessments", "Mentor students in lecture and laboratory courses") ) %>%
detailed_entries(what, when, with, where, why)

```


```{r employment, include = F}

# Old Employment Format

tribble(
  ~ role, ~ company, ~ location, ~ dates, 
   "Information Mountain Host Lead",  "Palisades Tahoe at Alpine Meadows", "Alpine Meadows, CA", "Oct 2023 - Current",
  #"Barista and Cashier", "Crest Cafe", "Alpine Meadows, CA", "July 2023 - Present", 
  "Adjunct Faculty, Biology Department", "Lake Tahoe Community College", "South Lake Tahoe, CA", "Jan 2023 - June 2024", 
  #"Hostess", "River Ranch Lodge and Restaurant", "Alpine Meadows, CA", "Aug 2021 - Present", 
  "Parking Supervisor", "Palisades Tahoe at Alpine Meadows", "Alpine Meadows, CA", "Nov 2020 - Jul 2023",
  #"Nursery Assistant", "Rock & Rose Nursery + Landscaping ", "Truckee, CA","Jun 2020 - Oct 2021",
  "Postdoctoral Scholar", " University of California, Davis", "Davis, CA", "May 2018 - Apr 2023",
  "Laboratory Manager", "The University of Texas at Austin", "Austin, TX", "Oct 2010 - Sep 2012", 
  "Teaching Specialist", "The University of Texas at Austin", "Austin, TX", "Jan 2007 - Dec 2010", 
) %>% 
  detailed_entries(role, dates, company, location)
```

# Computer Skills

Excel, HTML, LaTeX, Outlook, PowerPoint, Python, R, Square, TouchBistro, UNIX, Word     

# Languages Spoken

English, Spanish



```{r honors, include = F}

# Honors and Awards

tribble(
  ~Year, ~Type, ~Desc,
  "2019", "AAAS Community Engagement Fellowship", " ",
  "2019", "rstudio::conf 2019 Diversity Scholarship", " ",
  #"2017", "Outstanding Graduate Student Academic Employee Award", "  ",
  "2016, 17", "University Graduate Continuing Fellowship", " ",
  "2014, 15, 16", "Academic Enrichment Fund Award", " ",
 # "2013, 11, 15", "Honorable mention, National Science Foundation Graduate Research Fellowship", " ",
) %>% 
  vitae::detailed_entries(
    Type,
    Year, 
    Desc
  )

```


# Service

```{r service, include = TRUE}

tribble(
  ~Year, ~Type, ~Desc,
  "2023", "Yoga Instructor ", "Courage Project",
  #"2023", "Ambassador ", "5 Gyres",
  #"2019", "Coordinator", "I Can Science, a National Geographic Video Series",
  "2018", "Instructor Trainer", "The Carpentries",
  "2017", "Secretary", "Software Carpentry Steering Committee",
  "2016", "Poster Judge", "College of Natural Science Undergraduate Research Forum",
  "2012 - 17", "Coordinator", "Annual Big Data in Biology Symposium",
  "2014 - 16", "Coordinator", "Summer School for Big Data in Biology",
  "2014", "Coordinator", "Transdisciplinary Graduate Student Luncheon",
  "2009", "Spanish Translator", "INBio Park, Costa Rica",
  " ", "Peer-reviewer", "AAS  Open  Research; Behavioral Ecology; Genes, Genomes & Genetics; Genes, Brains & Behavior; Journal of Experimental Zoology Part A; Nature; Physiology & Behavior; Proceedings of the Royal Society B; rOpenSci",) %>% 
  vitae::brief_entries(
    Desc,
    Year, 
    Type
  )

```