---
name:  
surname: Rayna Harris, PhD
position: "          "
#address: "Alpine Meadows, CA"
phone: 512-657-2964
www: www.raynaharris.com
email: "raynaharris@palisadestahoe.com "
twitter: raynamharris
#github: raynamharris
linkedin: raynamharris
#date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
headcolor: 414141
docname: "`r format(Sys.time(), '%B %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(rorcid)
library(tidyverse)
```

# Professional Summary

I am interested in the Senior Strategy Analyst position at Alterra Mountain Company. I have worked at Palisades Tahoe at Alpine Meadows for four years in the Parking and Information Mountain Host Departments. I have a PhD in Cell and Molecular Biology and ten years of experience managing projects, analyzing data, and making data-driven decisions. My first-hand knowledge of Alterra mountains and ability to strategize and solve problems make me an excellent candidate for the Senior Strategy Analyst position.

# Education


```{r}

edu <- do.call("rbind",
  rorcid::orcid_educations("0000-0002-7943-5650")$`0000-0002-7943-5650`$`affiliation-group`$summaries
)
edu %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`,
    where = glue::glue("{`education-summary.organization.address.city`}, {`education-summary.organization.address.region`}")
  )
```

# Employment

```{r employment2}
tribble(
  ~ what, ~ when, ~ with, ~ where, ~why,
  "Information Mountain Host Lead", "Oct 2023 - Current",  "Palisades Tahoe at Alpine Meadows", "Alpine Meadows, CA", c("Provide a friendly and welcoming environment for guests and provide customer service", "Manage a small team of 3-5 employees and assist other departments as needed"),
 "Adjunct Faculty, Biology and Chemistry Departments", "Jan 2023 - June 2024", "Lake Tahoe Community College", "South Lake Tahoe, CA", c("Develop course syllabi, lesson plans, and assessments", "Mentor students in lecture and laboratory courses"),
 "Parking Supervisor", "Nov 2020 - Jul 2023", "Palisades Tahoe at Alpine Meadows",  "Alpine Meadows, CA", c("Analyzed parking data and model parking lot use trends", "Established parking structures and assisted with traffic flow"),
 "Postdoctoral Scholar", "May 2018 - Apr 2023", "The University of California, Davis", "Davis, CA", c("Managed large-scale, collaborative research projects", "Analyzed biomedical data, tested software, and generated technical reports")

   ) %>%
detailed_entries(what, when, with, where, why)

```


```{r employment, include = F}

# Old Employment Format

tribble(
  ~ role, ~ company, ~ location, ~ dates, 
   "Information Mountain Host Lead",  "Palisades Tahoe at Alpine Meadows", "Alpine Meadows, CA", "Oct 2023 - Current",
  #"Barista and Cashier", "Crest Cafe", "Alpine Meadows, CA", "July 2023 - Present", 
  "Adjunct Faculty, Biology Department", "Lake Tahoe Community College", "South Lake Tahoe, CA", "Jan 2023 - June 2024", 
  #"Hostess", "River Ranch Lodge and Restaurant", "Alpine Meadows, CA", "Aug 2021 - Present", 
  "Parking Supervisor", "Palisades Tahoe at Alpine Meadows", "Alpine Meadows, CA", "Nov 2020 - Jul 2023",
  #"Nursery Assistant", "Rock & Rose Nursery + Landscaping ", "Truckee, CA","Jun 2020 - Oct 2021",
  "Postdoctoral Scholar", " University of California, Davis", "Davis, CA", "May 2018 - Apr 2023",
  "Laboratory Manager", "The University of Texas at Austin", "Austin, TX", "Oct 2010 - Sep 2012", 
  "Teaching Specialist", "The University of Texas at Austin", "Austin, TX", "Jan 2007 - Dec 2010", 
) %>% 
  detailed_entries(role, dates, company, location)
```

# Computer Skills

Excel, HTML, LaTeX, Outlook, PowerPoint, Python, R, Square, TouchBistro, UNIX, Word     

# Languages Spoken

English, Spanish

# Honors and Awards

```{r honors, include = TRUE}

tribble(
  ~Year, ~Type, ~Desc,
  "2019", "AAAS Community Engagement Fellowship", " ",
  "2019", "rstudio::conf 2019 Diversity Scholarship", " ",
  #"2017", "Outstanding Graduate Student Academic Employee Award", "  ",
  "2016, 17", "University Graduate Continuing Fellowship", " ",
  "2014, 15, 16", "Academic Enrichment Fund Award", " ",
 # "2013, 11, 15", "Honorable mention, National Science Foundation Graduate Research Fellowship", " ",
) %>% 
  vitae::detailed_entries(
    Type,
    Year, 
    Desc
  )

```