---
name:  
surname: Rayna Harris, PhD
position: "          "
#address: "Alpine Meadows, CA"
phone: 512-657-2964
www: www.raynaharris.com
email: "raynaharris@palisadestahoe.com "
twitter: raynamharris
#github: raynamharris
linkedin: raynamharris
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
headcolor: 414141
docname: résumé
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(rorcid)
library(tidyverse)
```

# Professional Summary

I am interested in the Senior Strategy Analyst position at Alterra Mountain Company. I have worked at Palisades Tahoe at Alpine Meadows for four years in the Parking and Information Mountain Host Departments. I have a PhD in Cell and Molecular Biology and ten years of experience managing projects, analyzing data, and making data-driven decisions. My first-hand knowledge of Alterra mountains and ability to strategize and solve problems make me an excellent candidate for the Senior Strategy Analyst position.

# Education


```{r}

edu <- do.call("rbind",
  rorcid::orcid_educations("0000-0002-7943-5650")$`0000-0002-7943-5650`$`affiliation-group`$summaries
)
edu %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`,
    where = `education-summary.organization.address.city`
  )
```

# Employment

```{r employment}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, 
   "Blah, Blah, Blah",  "Palisades Tahoe at Alpine Meadows - Information Mountain Host Lead", "Alpine Meadows, CA", "Oct 2023 - Current",
  #"Barista and Cashier", "Crest Cafe", "Alpine Meadows, CA", "July 2023 - Present", 
  "Adjunct Faculty, Biology Department", "Lake Tahoe Community College", "South Lake Tahoe, CA", "Jan 2023 - June 2024", 
  #"Hostess", "River Ranch Lodge and Restaurant", "Alpine Meadows, CA", "Aug 2021 - Present", 
  "Parking Supervisor", "Palisades Tahoe at Alpine Meadows", "Alpine Meadows, CA", "Nov 2020 - Jul 2023",
  #"Nursery Assistant", "Rock & Rose Nursery + Landscaping ", "Truckee, CA","Jun 2020 - Oct 2021",
  "Postdoctoral Scholar", " University of California, Davis", "Davis, CA", "May 2018 - Apr 2023",
  "Laboratory Manager", "The University of Texas at Austin", "Austin, TX", "Oct 2010 - Sep 2012", 
  "Teaching Specialist", "The University of Texas at Austin", "Austin, TX", "Jan 2007 - Dec 2010", 
) %>% 
  detailed_entries(role, dates, company, loc)
```

# Computer Skills

Excel, HTML, LaTeX, Outlook, PowerPoint, Python, R, Square, TouchBistro, UNIX, Word     

# Languages Spoken

English, Spanish

# Honors and Awards

```{r honors, include = TRUE}

tribble(
  ~Year, ~Type, ~Desc,
  "2019", "AAAS Community Engagement Fellowship", " ",
  "2019", "rstudio::conf 2019 Diversity Scholarship", " ",
  "2017", "Outstanding Graduate Student Academic Employee Award", "  ",
  "2016, 17", "University Graduate Continuing Fellowship", " ",
  "2014, 15, 16", "Academic Enrichment Fund Award", " ",
 # "2013, 11, 15", "Honorable mention, National Science Foundation Graduate Research Fellowship", " ",
) %>% 
  vitae::detailed_entries(
    Type,
    Year, 
    Desc
  )

```