%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 8 February 2019
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,]{moderncv}

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'

\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{HTML}{000000}% custom
\definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey

\usepackage[scaled=0.86]{DejaVuSansMono}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\def\donothing#1{#1}
\def\emaillink#1{#1}

%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75,footskip=60pt]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvheadnamewidth}{10cm}            % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...



% personal data
\name{}{Rayna M. Harris, PhD}
\title{Science, Education, Community Engagement}


 % Phone number
\email{\donothing{\href{mailto:rayna.harris@gmail.com}{\nolinkurl{rayna.harris@gmail.com}}}}
\homepage{www.raynaharris.com} % Personal website






% \extrainfo{additional information}                 % optional, remove / comment the line if not wanted




% Pandoc CSL macros

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle



\hypertarget{education}{%
\section{Education}\label{education}}

\nopagebreak
    \cvitem{2012 - 2017}{Ph.D. Cell and Molecular Biology. The University of Texas at Austin}
    \cvitem{2002 - 2006}{B.S. Biochemistry. The University of Texas at Austin}

\hypertarget{certifications}{%
\section{Certifications}\label{certifications}}

\nopagebreak
    \cvitem{2024}{200-hour Hatha Yoga Teacher Training. Palisades Yoga, Olympic Valley, CA}

\hypertarget{experience}{%
\section{Experience}\label{experience}}

\nopagebreak
    \cvitem{2023 - 2024}{Adjunct Faculty. Lake Tahoe Community College}
    \cvitem{2021 - 2023}{Postdoctoral Scholar.  University of California, Davis}
    \cvitem{2020 - 2022}{Parking Supervisor. Alpine Meadows Ski Resort }
    \cvitem{2018 - 2020}{Postdoctoral Scholar.  University of California, Davis}
    \cvitem{2010 - 2012}{Laboratory Manager. The University of Texas at Austin}
    \cvitem{2007 - 2010}{Teaching Specialist. The University of Texas at Austin}

\hypertarget{honors-and-awards}{%
\section{Honors and Awards}\label{honors-and-awards}}

\nopagebreak
    \cvitem{2019}{AAAS Community Engagement Fellowship.  }
    \cvitem{2014, 15, 16}{Academic Enrichment Fund Award.  }

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\nopagebreak
    \cvitem{Spring 2024}{Principles of Biology III Lab (BIO 103). Lake Tahoe Community College}
    \cvitem{2023 - 2024}{Yoga Instructor. Courage Project}
    \cvitem{Spring 2023}{Organic Chemistry III Lab (CHM 223L). Lake Tahoe Community College}
    \cvitem{Spring 2023}{Cell and Molecular Biology (BIO 110). Lake Tahoe Community College}
    \cvitem{Winter 2023}{Principles of Biology III Lecture (BIO 103). Lake Tahoe Community College}
    \cvitem{2022}{Introduction to R. University of California, Davis}
    \cvitem{2022}{Introduction to Cloud Computing. University of California, Davis}
    \cvitem{2022}{Introduction to UNIX for Cloud Computing. University of California, Davis}
    \cvitem{2016 - 2019}{Instructor Training. The Carpentries}
    \cvitem{2017}{Biostatistics (SDS 328M). The University of Texas at Austin}
    \cvitem{2013}{Problems in Modern Biology (BIO 301E). The University of Texas at Austin}
    \cvitem{2007 - 2010}{Organic Chemistory Laboratory (CH 210C). The University of Texas at Austin}
    \cvitem{2008 - 2009}{Introduction to Spanish. Futura Language Professionals}

\hypertarget{selected-publications}{%
\section{Selected Publications}\label{selected-publications}}

\emph{Available at
\url{https://scholar.google.com/citations?user=_bVy9pMAAAAJ\&hl=en}}\\

\nopagebreak
    \cvitem{2022}{A Parigi, MC Lim, S Canchi, J Sanchez, J Walter, RM Harris, et al., A virtual training module for introducing the use of Amazon Web Services. Journal of Open Source Education 5 (54), 167}
    \cvitem{2021}{SH Austin, JS Krause, R Viernes, VS Farrar, AM Booth, RM Harris, et al., Uncovering the sex-specific endocrine responses to reproduction and parental care. Frontiers in Endocrinology 12, 631384}
    \cvitem{2020}{A Nederbragt, RM Harris, AP Hill, G Wilson, Ten quick tips for teaching with participatory live coding. PLoS Computational Biology 16 (9), e1008090}
    \cvitem{2019}{DJB Clarke, L Wang, A Jones, ML Wojciechowicz, D Torre, KM Jagodnik, et al., FAIRshake: Toolkit to Evaluate the FAIRness of Research Digital Resources. Cell systems 9 (5), 417-421}
    \cvitem{2019}{RM Harris, HY Kao, JM Alarcon, HA Hofmann, A Fenton, Hippocampal transcriptomic responses to enzyme‐mediated cellular dissociation. Hippocampus 153585}
    \cvitem{2018}{GA Devenyi, R Emonet, RM Harris, KL Hertweck, D Irving, I Milligan, et al., Ten simple rules for collaborative lesson development. PLOS Computational Biology 14 (3), e1005963}
    \cvitem{2016}{RM Harris, LA O’Connell, HA Hofmann, Brain Evolution, Development, and Plasticity. The Wiley Handbook of Evolutionary Neuroscience 422}
    \cvitem{2015}{RM Harris, HA Hofmann, Seeing is believing: Dynamic evolution of gene families. Proceedings of the National Academy of Sciences 112 (5), 1252-1253}
    \cvitem{2014}{D Brawand, CE Wagner, YI Li, M Malinsky, I Keller, S Fan, O Simakov, et al., The genomic substrate for adaptive radiation in African cichlid fish. Nature 513 (7518), 375–381}
    \cvitem{2014}{RM Harris, HA Hofmann, Neurogenomics of Behavioral Plasticity. Advances in Experimental Medicine and Biology 781, 149-168}

\hypertarget{service}{%
\section{Service}\label{service}}

\nopagebreak
    \cvitem{2023 - 2024}{Yoga Instructor . Courage Project}
    \cvitem{2018 - 2019}{Spanish Translator. The Carpentries}
    \cvitem{2017 - 2018}{Secretary. Software Carpentry Steering Committee}
    \cvitem{2016 - 2017}{Poster Judge. College of Natural Science Undergraduate Research Forum}
    \cvitem{2012 - 2017}{Coordinator. Annual Big Data in Biology Symposium}
    \cvitem{2014 - 2016}{Coordinator. Summer School for Big Data in Biology}
    \cvitem{2014}{Coordinator. Transdisciplinary Graduate Student Luncheon}
    \cvitem{2009}{Spanish Translator. INBio Park, Costa Rica}
    \cvitem{ }{Peer-reviewer. AAS  Open  Research; Behavioral Ecology; Genes, Genomes \& Genetics; Genes, Brains \& Behavior; Journal of Experimental Zoology Part A; Nature; Physiology \& Behavior; Proceedings of the Royal Society B; rOpenSci}


\end{document}

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
