---
#name:
surname: Dr. Rayna M. Harris
position: "SUP Yoga Instructor"
#address:  
phone: 512-657-2964
www: www.raynaharris.com/yoga/
email: "rayna.harris@gmail.com"
#twitter: raynamharris
#github: raynamharris
#linkedin: raynamharris
youtube: raynaharris8443
instagram: raynaharris
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
fontsize: 11pt
headcolor: "000000"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(rorcid)
library(tibble)
library(scholar)
library(tidyverse)
library(pkgsearch)
```

I bought my first paddle board in 2016 for the sole purpose to doing and teaching Stand-up Paddle (SUP) yoga. In 2023 I finally pursued and received a 200 hour Hatha Yoga certification, and I taught SUP yoga with Tahoe Flow Arts and Fitness at Mourelatos Lakeshore Resort the summer of 2024. I've take SUP yoga class with Kayla Mountain Lotus and Vinyasa yoga classes with Kellee at various locations. I would love to join the Mountain Lotus team to help with the SUP yoga classes and more.

# Education

```{r education, include = T}

tribble(
  ~Year, ~Type, ~Desc, 
  
  "2002 - 2006", "B.S", "Biochemistry, The University of Texas at Austin", 
  "2012 - 2017", "Ph.D", "Cell and Molecular Biology, The University of Texas at Austin",
  "2018 - 2023", "Postdoctoral Scholar", "University of California, Davis") %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  )

```

# Certification

```{r certification, include = T}

tribble(
  ~Year, ~Type, ~Desc, 
  "2025", "10-hour Art of Vinyasa Flow Certification", "Mountain Lotus, Truckee, CA", 
  "2023", "200-hour Hatha Yoga Certificatiton", "Palisades Yoga, Olympic Valley, CA",
  ) %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  )

```

# Current Employment

```{r experience, include = TRUE}

tribble(
  ~Year, ~Type, ~Desc,
  "Since 2024", "Yoga Instructor", "Tahoe Flow Arts & Fitness",
  "Since 2023", "Adjunct Faculty", "Lake Tahoe Community College",
  "Since 2020", "Parking Attendant", "Palisades Tahoe at Alpine",
  
) %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  ) 

```


# Yoga Teaching Experience

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  "2024 - 2025", "Hatha and Vinyasa Yoga", "Tahoe Flow Arts & Fitness, Ritz Carlton Northstar",
  "2024","Beach Yoga and Stand Up Paddle Yoga, Tahoe Flow Arts & Fitness", "Mourelatos Lakeshore Resort", 
  "2024", "Yoga Retreat", "La Fuerza Latina, Frog Lake Huts, Truckee, CA", 
  "Since 2023", "Mindful Yoga for Youth", "The Courage Project, various locations in Tahoe"
) %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  ) 
```



# Science Teaching Experience

```{r}
tribble(
  ~ with, ~ what, ~ when, 
  "Anatomy & Physiology Lab (BIO 203 - 205)", "Lake Tahoe Community College", "2024 - 2025", 
   "Dual Credit Chemistry (CHM 100)", "Lake Tahoe Community College and South Lake Tahoe High School", "Fall 2024", 
  "Organic Chemistry III Lab (CHM 223L)", "Lake Tahoe Community College", "Spring 2023", 
  "Cell and Molecular Biology (BIO 110)", "Lake Tahoe Community College", "Spring 2023", 
  "Principles of Biology III (BIO 103)", "Lake Tahoe Community College", "Winter 2023", 
  #"Introduction to R", "University of California, Davis", "2022", 
  #"Introduction to Cloud Computing", "University of California, Davis", "2022",
  "Introduction to UNIX for Cloud Computing", "University of California, Davis", "2022",
  "Instructor Training", "The Carpentries", "2016 - 2019",
  "Biostatistics (SDS 328M)", "The University of Texas at Austin", "2017", 
  "Problems in Modern Biology (BIO 301E)", "The University of Texas at Austin", "2013", 
  "Organic Chemistory Laboratory (CH 210C)", "The University of Texas at Austin",  "2007 - 2010",
) %>% 
  brief_entries(with, when, what)
```

