---
#name:
surname: Dr. Rayna M. Harris
position: "Education, Science, Community Engagement"
#address:  
#phone:  
www: raynamharris.com
#email: "rmharris@ucdavis.edu"
twitter: raynamharris
github: raynamharris
#linkedin: raynamharris
youtube: raynaharris8443
instagram: raynaharris
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
fontsize: 11pt
headcolor: "000000"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(rorcid)
library(tibble)
library(scholar)
library(tidyverse)
library(pkgsearch)
```

I am a passionate teacher and enjoy helping others. I have mostly taught science and computer classes to aspiring doctors and engineers. The older I get, though, I am less concerned with helping people achieve their career goals and more interested in helping people maintain a happy, healthy lifestyle. I want to be a Yoga instructor to help locals and tourists in the Tahoe community improve their flexibility, alignment, strength, mindset, and heart health. 



# Education

```{r education, include = T}

tribble(
  ~Year, ~Type, ~Desc, 
  
  "2002 - 2006", "B.S.", "Biochemistry, The University of Texas at Austin", 
  "2012 - 2017", "Ph.D.", "Cell and Molecular Biology, The University of Texas at Austin",
  "2018 - 2023", "Postdoctoral Scholar", "University of California, Davis") %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  )

```


# Current Employment

```{r experience, include = TRUE}

tribble(
  ~Year, ~Type, ~Desc,
  "2023 - 2023", "Adjunct Faculty", "Lake Tahoe Community College",
  "2021 - 2023", "Hostess", "River Ranch Lodge & Resturaunt",
  "2020 - 2023", "Parking Attendant", "Palisades Tahoe at Alpine",
  
) %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  ) 

```












# Teaching Experience

```{r}
tribble(
  ~ with, ~ what, ~ when, 
  "Organic Chemistry III Lab (CHM 223L)", "Lake Tahoe Community College", "Spring 2023", 
  "Cell and Molecular Biology (BIO 110)", "Lake Tahoe Community College", "Spring 2023", 
  "Principles of Biology III (BIO 103)", "Lake Tahoe Community College", "Winter 2023", 
  "Introduction to R", "University of California, Davis", "2022", 
  #"Introduction to Cloud Computing", "University of California, Davis", "2022",
  "Introduction to UNIX for Cloud Computing", "University of California, Davis", "2022",
  "Instructor Training", "The Carpentries", "2016 - 2019",
  "Biostatistics (SDS 328M)", "The University of Texas at Austin", "2017", 
  "Problems in Modern Biology (BIO 301E)", "The University of Texas at Austin", "2013", 
  "Organic Chemistory Laboratory (CH 210C)", "The University of Texas at Austin",  "2007 - 2010",
) %>% 
  brief_entries(with, when, what)
```

# Yoga Experience


```{r}
tribble(
  ~Year, ~Type, ~Desc,
  "10 hrs", "Palisades Yoga", "Olympic Valley, CA",
  "15 hrs", "Mountain Lotus Yoga", "Tahoe City, CA",
  "10 hrs", "Tahoe Yoga and Wellness Center", "Truckee, CA",
  "15 hrs", "Black Swan Yoga", "Austin, TX",
  "100 hrs", "BFree Yoga", "Austin, TX ",
  "100 hrs", "Yoga With Adriene", "Online ",

) %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  ) 
```

