---
#name:
surname: Dr. Rayna M. Harris
position: "SUP Yoga Instructor"
#address:  
phone: 512-657-2964
www: www.raynaharris.com/yoga/
email: "rayna.harris@gmail.com"
#twitter: raynamharris
#github: raynamharris
#linkedin: raynamharris
youtube: raynaharris8443
instagram: raynaharris
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
fontsize: 11pt
headcolor: "000000"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(rorcid)
library(tibble)
library(scholar)
library(tidyverse)
library(pkgsearch)
```

I bought my first paddle board in 2016 with the vision of eventually teaching Stand-up Paddle (SUP) yoga. In 2023 I  pursued and received a 200-hour Hatha Yoga certification, and I taught SUP yoga with Tahoe Flow Arts and Fitness at Mourelatos Lakeshore Resort in 2024. I've taken SUP yoga classes with Kayla at Mountain Lotus, and I would love to join the Mountain Lotus team to teach SUP yoga classes and more!

# Education

```{r education, include = T}

tribble(
  ~Year, ~Type, ~Desc, 
  
  "2002 - 2006", "B.S", "Biochemistry, The University of Texas at Austin", 
  "2012 - 2017", "Ph.D", "Cell and Molecular Biology, The University of Texas at Austin",
  "2018 - 2023", "Postdoctoral Scholar", "University of California, Davis") %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  )

```

# Certification

```{r certification, include = T}

tribble(
  ~Year, ~Type, ~Desc, 
  "2025", "10-hour Art of Vinyasa Flow Certification", "Mountain Lotus, Truckee, CA", 
  "2023", "200-hour Hatha Yoga Certificatiton", "Palisades Yoga, Olympic Valley, CA",
  ) %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  )

```

# Current Employment

```{r experience, include = TRUE}

tribble(
  ~Year, ~Type, ~Desc,
  "2025", "Yoga Instructor", "Sport Haus at Sugar Bowl",
  "Since 2024", "Yoga Instructor", "Tahoe Flow Arts & Fitness",
  "Since 2023", "Adjunct Faculty", "Lake Tahoe Community College",
  "Since 2020", "Parking Attendant", "Palisades Tahoe at Alpine",
  
) %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  ) 

```


# Yoga Teaching Experience

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  "2025", "Restorative Yoga", "Sport Haus at Sugar Bowl",
  "2024 - 2025", "Hatha and Vinyasa Yoga", "Tahoe Flow Arts & Fitness, Ritz Carlton Northstar",
  "2024","Beach Yoga and Stand Up Paddle Yoga, Tahoe Flow Arts & Fitness", "Mourelatos Lakeshore Resort", 
  "2024", "Yoga Retreat", "La Fuerza Latina, Frog Lake Huts, Truckee, CA", 
  "Since 2023", "Mindful Yoga for Youth", "The Courage Project, various locations in Tahoe"
) %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  ) 
```


# Service

```{r service, include = TRUE}

tribble(
  ~Year, ~Type, ~Desc,
  "2023 - 2025", "Volunteer Yoga Instructor ", " The Courage Project",
  ) %>% 
  vitae::brief_entries(
    Desc,
    Year, 
    Type
  )

```


