---
#name:
surname: Rayna Harris,
position: "Yoga Instructor"
#address:  
phone: 512-657-2964
www: www.raynaharris.com/yoga/
email: "rayna.harris@gmail.com"
#twitter: raynamharris
#github: raynamharris
#linkedin: raynamharris
youtube: raynaharris8443
instagram: raynaharris
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
fontsize: 11pt
headcolor: "000000"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(rorcid)
library(tibble)
library(scholar)
library(tidyverse)
library(pkgsearch)
```

I am interested in the opportunity to contribute as a Yoga Instructor at Palisades Yoga, where the community, instructors, and location create an ideal environment for sharing the practice of yoga. With two years of teaching experience through the Courage Project and an additional year at Tahoe Flow Arts and Fitness, I feel prepared to lead engaging and mindful classes. I would be happy to take on a regular class, such as Restore & Flow or Hatha Flow, and I’m also available to substitute for Candlelight Vinyasa and Yoga for Strength as needed.    

$\\$

# Education

```{r education, include = T}

tribble(
  ~Year, ~Type, ~Desc, 
  "2018 - 2023", "Postdoctoral Scholar", "University of California, Davis",
  "2012 - 2017", "Ph.D", "Cell and Molecular Biology, The University of Texas at Austin",
  "2002 - 2006", "B.S", "Biochemistry, The University of Texas at Austin") %>%
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  )

```

# Certification

```{r certification, include = T}

tribble(
  ~Year, ~Type, ~Desc, 
  "2025", "10-hour Art of Vinyasa Flow Certification", "Mountain Lotus, Truckee, CA", 
  "2023", "200-hour Hatha Yoga Certificatiton", "Palisades Yoga, Olympic Valley, CA",
  ) %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  )

```

# Current Employment

```{r experience, include = TRUE}

tribble(
  ~Year, ~Type, ~Desc,
  "Winter 2025", "Yoga Instructor", "Sport Haus at Sugar Bowl",
  "Since 2024", "Yoga Instructor", "Tahoe Flow Arts & Fitness",
  "Since 2023", "Adjunct Faculty", "Lake Tahoe Community College",
  "Since 2020", "Parking Attendant", "Palisades Tahoe at Alpine",
  
) %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  ) 

```


# Yoga Teaching Experience

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  "2025", "Restorative Yoga", "Sport Haus at Sugar Bowl",
  "2024 - 2025", "Hatha and Vinyasa Yoga", "Tahoe Flow Arts & Fitness, Ritz Carlton Northstar",
  "2024","Beach Yoga and Stand Up Paddle Yoga, Tahoe Flow Arts & Fitness", "Mourelatos Lakeshore Resort", 
  "2024", "Yoga Retreat", "La Fuerza Latina, Frog Lake Huts, Truckee, CA", 
  "Since 2023", "Mindful Yoga for Youth", "The Courage Project, various locations in Tahoe"
) %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  ) 
```


# Service

```{r service, include = TRUE}

tribble(
  ~Year, ~Type, ~Desc,
  "2023 - 2025", "Volunteer Yoga Instructor ", " The Courage Project",
  ) %>% 
  vitae::brief_entries(
    Desc,
    Year, 
    Type
  )

```


